Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-01 paper/main.tex
splitting out continuity and equivariance

\subsection{Natural Transformation of Data to Graphic}
\label{sec:artist:category}

@@

We model data as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)", shift left = 10.5, color=sheaf] &   
\end{tikzcd}
\end{equation}

The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

\note{Should this move to down where we describe equivariance? It's not used at all currently in this section}
\begin{definition} 
  \label{def:category:F} The fiber category $\mathcal{\dfiberc}$ is a monoidal category\cite{milewskiCategoryTheoryProgrammers}, which means it is a category equipped with a bifunctur $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$
  \begin{itemize}
    \item \textit{object} a monoid object \dfiber. A monoid is a set with a binary operator that is associative, closed, and for which the set contains an identity element $i$ \cite{nlan:monoid}.
    \item \textit{morphisms} $\dfiber \otimes \dfiber \rightarrow \dfiber$ and unit $i \rightarrow \dfiber$
  \end{itemize}
\end{definition}
The bifunctor $\otimes$ combines categories in a way that  preserves identity and composition \cite{fongInvitationAppliedCategory2019}. For example, given a pair of categories $\mathcal{\dfiber_a},\mathcal{\dfiber_b}$, the bifunctor yields a set of pairs $\{(\dfiber_a, \dfiber_b) | \dfiber_a \in \mathcal{\dfiber_a}, \dfiber_b \in \mathcal{\dfiber_b}\}$. For the associated morphisms $g: \mathcal{\dfiber_a}\rightarrow \mathcal{\dfiber_a}$ and $h: \mathcal{\dfiber_b}\rightarrow \mathcal{\dfiber_b}$, the function $(g\times h): (\mathcal{\dfiber_a}\times \mathcal{\dfiber_b}) \rightarrow (\mathcal{\dfiber_a}\times \mathcal{\dfiber_b})$ is pointwise $(g\times h)(\dfiber_a, \dfiber_b)\coloneqq (g(\dfiber_a), h(\dfiber_b))$. Because of the bifunctor, objects of the category $\mathcal{\dfiber}$ can be the product of any arbitrary number and types of categories, including \textbf{Set}, \textbf{Graph}, and topological spaces \textbf{Top}.

@@

\note{is artist functor by virtue of being natural transform or do we define artist as functor between functors}

>>>>

\subsection{Continuity}
\label{sec:artist:category}

@@

We model data as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)", shift left = 10.5, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

@@

\subsection{Equivariance}

\begin{definition} 
  \label{def:category:F} The fiber category $\mathcal{\dfiberc}$ is a monoidal category\cite{milewskiCategoryTheoryProgrammers}, which means it is a category equipped with a bifunctur $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$
  \begin{itemize}
    \item \textit{object} a monoid object \dfiber. A monoid is a set with a binary operator that is associative, closed, and for which the set contains an identity element $i$ \cite{nlan:monoid}.
    \item \textit{morphisms} $\dfiber \otimes \dfiber \rightarrow \dfiber$ and unit $i \rightarrow \dfiber$
  \end{itemize}
\end{definition}
The bifunctor $\otimes$ combines categories in a way that  preserves identity and composition \cite{fongInvitationAppliedCategory2019}. For example, given a pair of categories $\mathcal{\dfiber_a},\mathcal{\dfiber_b}$, the bifunctor yields a set of pairs $\{(\dfiber_a, \dfiber_b) | \dfiber_a \in \mathcal{\dfiber_a}, \dfiber_b \in \mathcal{\dfiber_b}\}$. For the associated morphisms $g: \mathcal{\dfiber_a}\rightarrow \mathcal{\dfiber_a}$ and $h: \mathcal{\dfiber_b}\rightarrow \mathcal{\dfiber_b}$, the function $(g\times h): (\mathcal{\dfiber_a}\times \mathcal{\dfiber_b}) \rightarrow (\mathcal{\dfiber_a}\times \mathcal{\dfiber_b})$ is pointwise $(g\times h)(\dfiber_a, \dfiber_b)\coloneqq (g(\dfiber_a), h(\dfiber_b))$. Because of the bifunctor, objects of the category $\mathcal{\dfiber}$ can be the product of any arbitrary number and types of categories, including \textbf{Set}, \textbf{Graph}, and topological spaces \textbf{Top}.

\note{}
